Matching bullets

### 2015-11-17 imaging-paper.Rnw
Work on the loess section

1. Fix an x coordinate value.
2. Remove values from $y \in \{0, 100\}$ and $y \in \{900, 1000\}$.
3. For each y value from 100 to 900, compute a rolling average to smooth out any deviations occurring near the minimums.
4. Determine the minimum in the first half (corresponding to the left groove) and the minimum in the right half (corresponding to the right groove)
5. Remove all y values below the minimum and above the maximum

>>>>

\begin{enumerate}
    \item Fix an x coordinate value.
    \item Remove values from $y \in \{0, 100\}$ and $y \in \{900, 1000\}$.
    \item For each y value from 100 to 900, compute a rolling average to smooth out any deviations occurring near the minimums.
    \item Determine the minimum in the first half (corresponding to the left groove) and the minimum in the right half (corresponding to the right groove)
    \item Remove all y values below the minimum and above the maximum
\end{enumerate}

Next, we fit a Loess regression to the data

<<loess_fit, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit for part 1 of bullet 1', fig.pos='H', message=FALSE>>=
br111 <- get_bullet(file.path("GitHub", "x3prproto", "images", "Hamby252_3DX3P1of2", "Br1 Bullet 1-1.x3p"))
br111.groove <- get_grooves(br111)

my.loess <- fit_loess(br111, br111.groove)

my.loess$fitted
@

<<loess_resid, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit residuals for part 1 of bullet 1', fig.pos='H'>>=
my.loess <- fit_loess(br111, br111.groove)

my.loess$resid
@
